Constraint result to the self-interacting dark matter particle mass from the observational data

### 2025-05-14 article/article.tex
change the figure shows

   \title{Constraint result to the self-interacting dark matter model without dark energy
   in cosmology}

@@

   In this paper, we use the newly revised data from $H(z)$, supernovae Ia, 
   quasars and baryon acoustic oscillation by using the Markov chain Monte
   Carlo (MCMC) method. The result gives that the lower limit of the interacting
   dark matter particle mass is about 1 eV.

@@

   To constrain the relevant IDM models (\cite{Basilakos_2009}), we use the newly revised
   observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001, Daniel.Stern_2010, 
   M.Moresco_2012, Zhang_2014, Moresco_2016, 10.1093/mnras/stx301, 10.1093/mnrasl/slv037, 
   Borghi_2022, Jiao_2023}), the Pantheon+ set of 1701 SNe Ia 
   (\cite{Scolnic_2022}), the quasar data from \cite{Lusso_2020}, 
   the BAO data from SDSS-IV (\cite{PhysRevD.103.083533}) and DESI DR2 
   (\cite{desicollaboration2025desidr2resultsii}).

@@

   \begin{table}[htbp]
      \centering
      \begin{tabular}{ccl}
         \hline\hline
         $z$ & $H(z)$ & Reference \\
         \hline     
         0.07 & $69 \pm 19.6$ & \cite{Zhang_2014} \\
         0.09 & $69 \pm 12$ & \cite{PhysRevD.71.123001} \\
         0.12 & $68.6 \pm 26.2$ & \cite{Zhang_2014} \\
         0.17 & $83 \pm 8$ & \cite{PhysRevD.71.123001} \\
         0.179 & $75 \pm 4$ & \cite{M.Moresco_2012} \\
         0.199 & $75 \pm 5$ & \cite{M.Moresco_2012} \\
         0.2 & $72.9 \pm 29.6$ & \cite{Zhang_2014} \\
         0.27 & $77 \pm 14$ & \cite{PhysRevD.71.123001} \\
         0.28 & $88.8 \pm 36.6$ & \cite{Zhang_2014} \\
         0.352 & $83 \pm 14$ & \cite{M.Moresco_2012} \\
         0.3802 & $83 \pm 13.5$ & \cite{Moresco_2016}  \\
         0.4 & $95 \pm 17$ & \cite{PhysRevD.71.123001} \\
         0.4004 & $77 \pm 10.2$ & \cite{Moresco_2016} \\
         0.4247 & $87.1 \pm 11.2$ & \cite{Moresco_2016} \\
         0.4497 & $92.8 \pm 12.9$ & \cite{Moresco_2016} \\
         0.47 & $89 \pm 34$ & \cite{10.1093/mnras/stx301} \\
         0.4783 & $80.9 \pm 9$ & \cite{Moresco_2016} \\
         0.48 & $97 \pm 62$ & \cite{Daniel.Stern_2010} \\
         0.593 & $104 \pm 13$ & \cite{M.Moresco_2012} \\
         0.68 & $92 \pm 8$ & \cite{M.Moresco_2012} \\
         0.75 & $98.8 \pm 33.6$ & \cite{Borghi_2022} \\
         0.781 & $105 \pm 12$ & \cite{M.Moresco_2012} \\
         0.8 & $113.1 \pm 15.1$ & \cite{Jiao_2023} \\
         0.875 & $125 \pm 17$ & \cite{M.Moresco_2012} \\
         0.88 & $90 \pm 40$ & \cite{Daniel.Stern_2010} \\
         0.9 & $117 \pm 23$ & \cite{PhysRevD.71.123001} \\
         1.037 & $154 \pm 20$ & \cite{M.Moresco_2012} \\
         1.3 & $168 \pm 17$ & \cite{PhysRevD.71.123001} \\
         1.363 & $160 \pm 33.6$ & \cite{10.1093/mnrasl/slv037} \\
         1.43 & $177 \pm 18$ & \cite{PhysRevD.71.123001} \\
         1.53 & $140 \pm 14$ & \cite{PhysRevD.71.123001} \\
         1.75 & $202 \pm 40$ & \cite{PhysRevD.71.123001} \\
         1.965 & $186.5 \pm 50.4$ & \cite{10.1093/mnrasl/slv037} \\
         \hline    
      \end{tabular}
      \caption{The OHD dataset from different reference.}
      \label{tab:1}
   \end{table}

@@

\subsection{Quasar}

   The quasar gives a higher redshift than SNe Ia.
   We use the QSO dataset from \cite{Lusso_2020}, which gives
   2421 samples with the ultraviolet (UV) and X-ray luminosity.
   The redshift is up to $\simeq7.5$.

   The $L_X-L_{UV}$ relation of quasar is usually written as
   \begin{equation}
      \log_{10}(L_X)=\beta+\gamma\log_{10}(L_{UV}),
   \end{equation}
   which gives that
   \begin{eqnarray}
      \nonumber\log_{10}(F_X)&=\beta+(\gamma-1)\log_{10}(4\pi)+\gamma\log_{10}(F_{UV})
                    \\ &+2(\gamma-1)\log_{10}(d_L),
   \end{eqnarray}
   where $d_L$ is the luminosity distance same as Eq.(\ref{eq:15}).
   Here we use the parameters defined in \cite{li2024redshiftevolutionxrayuv}, which
   gives\begin{equation}
      \beta=\beta_0+\beta_1(1+z),\gamma=\gamma_0+\gamma_1(1+z),
   \end{equation}
   so the $\chi^2$ function for the QSO data can be defined as
   \begin{equation}
      \chi_{\text{QSO}}^2=\sum_i\left[\frac{(y_{\text{th}}^2-y_{\text{data}}^2)}{s_i^2}
      -\ln(2\pi s_i^2)\right],
   \end{equation}
   where $s_i^2=\mathrm{d}y_i^2+\gamma^2\mathrm{d}x_i^2+\delta^2$ refers to the 
   uncertainties on the $x_i\ (\log_{10}F_X)$ and $y_i\ (\log_{10}F_{UV})$ and
   $\delta_i$ reprensent the instrinsic dispersion.

@@

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccc}
         \hline\hline
         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
         \hline
         MGS & 0.15 & $4.51 \pm 0.14$ & --- & --- \\
         BOSS galaxy & 0.38 & --- & $10.27 \pm 0.15$ & $24.89 \pm 0.58$ \\
         BOSS galaxy & 0.51 & --- & $13.38 \pm 0.18$ & $22.43 \pm 0.48$ \\
         eBOSS LRG & 0.70 & --- & $17.65 \pm 0.30$ & $19.78 \pm 0.46$ \\
         eBOSS ELG & 0.85 & --- & $19.5 \pm 1.0$ & $19.6 \pm 2.1$ \\
         eBOSS quasar& 1.48 & --- & $30.21 \pm 0.79$ & $13.23 \pm 0.47$ \\
         Ly$\alpha$-Ly$\alpha$ & 2.33 & --- & $37.6 \pm 1.9$ & $8.93 \pm 0.28$ \\
         Ly$\alpha$-quasar & 2.33 & --- & $37.3 \pm 1.7$ & $9.08 \pm 0.34$ \\
         \hline
      \end{tabular}
      \caption{The BAO+RSD measurements dataset from SDSS-IV.}
      \label{tab:2}
   \end{table*}

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccc}
         \hline\hline
         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
         \hline
         BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
         LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
         LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
         LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
         ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
         QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
         Ly$\alpha$ & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
         \hline
         LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
         ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
         \hline
      \end{tabular}
      \caption{The BAO dataset from DESI DR2.}
      \label{tab:3}
   \end{table*}

@@

   \begin{table}[htbp]
      \centering
      \begin{tabular}{lll}
         \hline\hline
         parameter & initial & prior \\
         \hline
         $\Omega_{2,0}$ & 0.3 & $\mathcal{U}[0.0,1.0]$ \\
         $n$ & 0 & $\mathcal{U}[-10,10]$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
         $H_0$[km/s/Mpc] & 70 & $\mathcal{U}[60,80]$ \\
         \hline
         $\beta_0$ & 6 & $\mathcal{U}[-15,15]$ \\
         $\beta_1$ & 1 & $\mathcal{U}[-10,10]$ \\
         $\gamma_0$ & 0.6 & $\mathcal{U}[0.0,1.0]$ \\
         $\gamma_1$ & 0 & $\mathcal{U}[-1.0,1.0]$ \\         
         $\delta$ & 0.2 & $\mathcal{U}[0.0,1.0]$ \\
         \hline
         $r_{\text{d}}h$[Mpc] & 100 & $\mathcal{U}[50,150]$ \\
         \hline
      \end{tabular}
      \caption{Parameters and priors used in analysis. 
      All of the priors are flat in the ranges given. 
      The $\log_{10}(\kappa C_1)$ does not have a predicted value, 
      and the initial value of each chain is selected randomly uniformly
      within the prior range.}
      \label{tab:4}
   \end{table}

@@

   We use the 97.7\% and 2.3\% quantiles (about $2\sigma$) to determine the upper and lower
   limits of the parameters. The  constraint results are shown in 
   Figure \ref{fig:1}-\ref{fig:5} and summarized in Table \ref{tab:5}.

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_2.pdf}
      }
      \caption{The constraint result from the observational
      $H(z)$ data.}
      \label{fig:1}
   \end{figure}

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{compare_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{compare_2.pdf}
      }
      \caption{The constraint result from the supernovae Ia data
      compared with the SNe Ia+QSO data.}
   \end{figure}

   We could find that the combined result of SNe Ia and QSO is quite
   similar to SNe Ia result, what may refer that the QSO cannot
   give an effective constraint. It may be due to the data quality
   at the high redshift, while the effective redshift of QSO as tracers in BAO
   is about 1.5, respectively, within the SNe Ia range.

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_2.pdf}
      }
      \caption{The constraint result from the SNe Ia + OHD data.}
   \end{figure}

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{bao_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{bao_2.pdf}
      }
      \caption{The constraint result from the BAO data.}
   \end{figure}

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_2.pdf}
      }
      \caption{The constraint result from the BAO + SNe Ia + OHD data.}
      \label{fig:5}
   \end{figure}

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccccc}
         \hline\hline
         Model 1 & OHD & SNe Ia & SNe Ia + QSO 
         & SNe Ia + OHD & BAO & BAO + SNe Ia + OHD \\
         \hline
         $\Omega_{2,0}$ & $0.324_{-0.066}^{+0.056}$ & $0.380_{-0.020}^{+0.020}$
          & $0.378_{-0.020}^{+0.020}$ & $0.375_{-0.019}^{+0.019}$
          & $0.298_{-0.007}^{+0.007}$ & $0.308_{-0.007}^{+0.005}$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.08$ & $<-2.73$ & $<-2.75$
         & $<-2.91$ & $<-3.38$  & $<-3.71$ \\
         $\log_{10}(M_x/$GeV) & $>-9.85$ & $>-9.26$ & $>-9.23$
         & $>-9.13$ & $>-8.56$ & $>-8.26$ \\
         \hline
      \end{tabular}
      \caption{The constraint results of Model 1.}
      \label{tab:5}
   \end{table*}

   \begin{figure}[htbp]
      \centering
      \includegraphics[width=0.45\textwidth]{pdf_1.pdf}
      \caption{The probability density of $\Omega_{2,0}$ from different
      datasets.}
      \label{fig:6}
   \end{figure}

   Fig \ref{fig:6} shows the difference between classical dataset ($H(z)$, SNe Ia)
   and newly released BAO dataset. The BAO dataset gives a strict constraint to
   $\Omega_{2,0} \simeq 0.3$, lower than the SNe Ia dataset about $3\sigma$, which
   gives a higher value $\Omega_{2,0} \simeq 0.4$. The constraint result to Pantheon+
   SNe Ia dataset in $\Lambda$CDM model is $\Omega_M \simeq 0.33$ (\cite{Borghi_2022}),

@@

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_widm_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_widm_2.pdf}
      }
      \caption{The constraint result from the observational
      $H(z)$ data.}
   \end{figure}

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{sne_widm_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{sne_widm_2.pdf}
      }
      \caption{The constraint result from the supernovae
      Ia data.}
   \end{figure}

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{sne_qso_widm_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{sne_qso_widm_2.pdf}
      }
      \caption{The constraint result from the SNe Ia + QSO data.}
   \end{figure}

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_widm_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_widm_2.pdf}
      }
      \caption{The constraint result from the OHD + SNe Ia data.}
   \end{figure}

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{bao_widm_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{bao_widm_2.pdf}
      }
      \caption{The constraint result from the BAO data.}
   \end{figure}

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_widm_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_sne_bao_widm_2.pdf}
      }
      \caption{The constraint result from the OHD + SNe Ia + BAO data.}
   \end{figure}

   The results from three dataset are different

   \begin{table*}[htbp]
      \centering
      \begin{tabular}{lcccccc}
         \hline\hline
         Model 2 & OHD & SNe Ia & SNe Ia + QSO 
         & OHD + SNe Ia & BAO & OHD + SNe Ia + BAO \\
         \hline
         $\Omega_{2,0}$ & $0.299_{-0.074}^{+0.074}$ & $0.216_{-0.078}^{+0.096}$
          & $0.208_{-0.087}^{+0.12}$ & $0.202_{-0.049}^{+0.060}$ 
          & $0.296_{-0.014}^{+0.014}$ & $0.291_{-0.013}^{+0.013}$ \\
         $n$ & $1.5_{-2.9}^{+1.4}$ & $-0.82_{-0.44}^{+0.29}$
          & $-0.85_{-0.49}^{+0.42}$ & $-0.83_{-0.27}^{+0.24}$
          & $-0.40_{-0.29}^{+0.29}$ & $-0.41_{-0.13}^{+0.13}$ \\
         $w_{\text{IDM}}$ & $-1.5_{-0.5}^{+1.0}$ & $-0.73_{-0.10}^{+0.15}$
          & $-0.72_{-0.14}^{+0.16}$ & $-0.72_{-0.08}^{+0.09}$
          & $-0.87_{-0.10}^{+0.10}$ & $-0.86_{-0.04}^{+0.04}$ \\
         \hline
      \end{tabular}
      \caption{The constraint results of Model 2.}
      \label{tab:6}
   \end{table*}

@@

   \begin{equation}
      Const=\mathcal{F}(-\infty)\equiv\lim_{x\to-\infty}\mathcal{F}(x)=
      \frac{\kappa C_1\ln\kappa C_1}{9H_0^4\Omega_{1,0}^2-4H_0^2\Omega_{1,0}(\kappa C_1)^2}.
   \end{equation}
   The initial time of today $t_0$ can be easily given as
   \begin{equation}
      t_0=2H_0^2\Omega_{1,0}[\mathcal{F}(-\infty)-\mathcal{F}(-H_0)],
   \end{equation}
   and the redshift $z_{\max}$ can be calculated as
   \begin{equation}
      z_{\max}=\exp\left[2H_0^2\Omega_{1,0}\int_{-\infty}^{-H_0}[\mathcal{F}(-\infty)
      -\mathcal{F}(x)]\mathrm{d}x+H_0t_0\right]-1,
   \end{equation}
   and $z_{\max}$ is also a function of $\Omega_{2,0}, \kappa C_1$ and $H_0$.
   \begin{figure}[htbp]
      \centering
      \includegraphics[width=0.7\textwidth]{zmax.pdf}
      \caption{The redshift $z_{\max}$ as $H_0=70$ km/s/Mpc}
   \end{figure}

>>>>

   \title{Constraint result to the self-interacting dark matter particle mass from the
   observational data}

@@

   In this paper, we use the newly revised data from $H(z)$, supernovae Ia 
   and baryon acoustic oscillation by using the Markov chain Monte
   Carlo (MCMC) method. The result gives that the lower limit of the interacting
   dark matter particle mass is about 10 eV.

@@

   To constrain the relevant IDM models (\cite{Basilakos_2009}), we use the newly revised
   observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001, Daniel.Stern_2010, 
   M.Moresco_2012, Zhang_2014, Moresco_2016, 10.1093/mnras/stx301, 10.1093/mnrasl/slv037, 
   Borghi_2022, Jiao_2023}), the Pantheon+ set of 1701 SNe Ia 
   (\cite{Scolnic_2022}), the BAO data from SDSS-IV (\cite{PhysRevD.103.083533}) and DESI DR2 
   (\cite{desicollaboration2025desidr2resultsii}).

@@

   \begin{table}
      \centering
      \begin{tabular}{ccl}
         \hline\hline
         $z$ & $H(z)$ & Reference \\
         \hline     
         0.07 & $69 \pm 19.6$ & \cite{Zhang_2014} \\
         0.09 & $69 \pm 12$ & \cite{PhysRevD.71.123001} \\
         0.12 & $68.6 \pm 26.2$ & \cite{Zhang_2014} \\
         0.17 & $83 \pm 8$ & \cite{PhysRevD.71.123001} \\
         0.179 & $75 \pm 4$ & \cite{M.Moresco_2012} \\
         0.199 & $75 \pm 5$ & \cite{M.Moresco_2012} \\
         0.2 & $72.9 \pm 29.6$ & \cite{Zhang_2014} \\
         0.27 & $77 \pm 14$ & \cite{PhysRevD.71.123001} \\
         0.28 & $88.8 \pm 36.6$ & \cite{Zhang_2014} \\
         0.352 & $83 \pm 14$ & \cite{M.Moresco_2012} \\
         0.3802 & $83 \pm 13.5$ & \cite{Moresco_2016}  \\
         0.4 & $95 \pm 17$ & \cite{PhysRevD.71.123001} \\
         0.4004 & $77 \pm 10.2$ & \cite{Moresco_2016} \\
         0.4247 & $87.1 \pm 11.2$ & \cite{Moresco_2016} \\
         0.4497 & $92.8 \pm 12.9$ & \cite{Moresco_2016} \\
         0.47 & $89 \pm 34$ & \cite{10.1093/mnras/stx301} \\
         0.4783 & $80.9 \pm 9$ & \cite{Moresco_2016} \\
         0.48 & $97 \pm 62$ & \cite{Daniel.Stern_2010} \\
         0.593 & $104 \pm 13$ & \cite{M.Moresco_2012} \\
         0.68 & $92 \pm 8$ & \cite{M.Moresco_2012} \\
         0.75 & $98.8 \pm 33.6$ & \cite{Borghi_2022} \\
         0.781 & $105 \pm 12$ & \cite{M.Moresco_2012} \\
         0.8 & $113.1 \pm 15.1$ & \cite{Jiao_2023} \\
         0.875 & $125 \pm 17$ & \cite{M.Moresco_2012} \\
         0.88 & $90 \pm 40$ & \cite{Daniel.Stern_2010} \\
         0.9 & $117 \pm 23$ & \cite{PhysRevD.71.123001} \\
         1.037 & $154 \pm 20$ & \cite{M.Moresco_2012} \\
         1.3 & $168 \pm 17$ & \cite{PhysRevD.71.123001} \\
         1.363 & $160 \pm 33.6$ & \cite{10.1093/mnrasl/slv037} \\
         1.43 & $177 \pm 18$ & \cite{PhysRevD.71.123001} \\
         1.53 & $140 \pm 14$ & \cite{PhysRevD.71.123001} \\
         1.75 & $202 \pm 40$ & \cite{PhysRevD.71.123001} \\
         1.965 & $186.5 \pm 50.4$ & \cite{10.1093/mnrasl/slv037} \\
         \hline    
      \end{tabular}
      \caption{The OHD dataset from different reference.}
      \label{tab:1}
   \end{table}

@@

@@

   \begin{table*}
      \centering
      \begin{tabular}{lcccc}
         \hline\hline
         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
         \hline
         MGS & 0.15 & $4.51 \pm 0.14$ & --- & --- \\
         BOSS galaxy & 0.38 & --- & $10.27 \pm 0.15$ & $24.89 \pm 0.58$ \\
         BOSS galaxy & 0.51 & --- & $13.38 \pm 0.18$ & $22.43 \pm 0.48$ \\
         eBOSS LRG & 0.70 & --- & $17.65 \pm 0.30$ & $19.78 \pm 0.46$ \\
         eBOSS ELG & 0.85 & --- & $19.5 \pm 1.0$ & $19.6 \pm 2.1$ \\
         eBOSS quasar& 1.48 & --- & $30.21 \pm 0.79$ & $13.23 \pm 0.47$ \\
         Ly$\alpha$-Ly$\alpha$ & 2.33 & --- & $37.6 \pm 1.9$ & $8.93 \pm 0.28$ \\
         Ly$\alpha$-quasar & 2.33 & --- & $37.3 \pm 1.7$ & $9.08 \pm 0.34$ \\
         \hline
      \end{tabular}
      \caption{The BAO+RSD measurements dataset from SDSS-IV.}
      \label{tab:2}
   \end{table*}

   \begin{table*}
      \centering
      \begin{tabular}{lcccc}
         \hline\hline
         Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
         \hline
         BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
         LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
         LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
         LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
         ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
         QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
         Ly$\alpha$ & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
         \hline
         LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
         ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
         \hline
      \end{tabular}
      \caption{The BAO dataset from DESI DR2.}
      \label{tab:3}
   \end{table*}

@@

   \begin{table}
      \centering
      \begin{tabular}{lll}
         \hline\hline
         parameter & initial & prior \\
         \hline
         $\Omega_{2,0}$ & 0.3 & $\mathcal{U}[0.0,1.0]$ \\
         $n$ & 0 & $\mathcal{U}[-10,10]$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
         $H_0$[km/s/Mpc] & 70 & $\mathcal{U}[60,80]$ \\
         \hline
         $r_{\text{d}}h$[Mpc] & 100 & $\mathcal{U}[50,150]$ \\
         \hline
      \end{tabular}
      \caption{Parameters and priors used in analysis. 
      All of the priors are flat in the ranges given. 
      The $\log_{10}(\kappa C_1)$ does not have a predicted value, 
      and the initial value of each chain is selected randomly uniformly
      within the prior range.}
      \label{tab:4}
   \end{table}

@@

   We use the 97.7\% and 2.3\% quantiles (about $2\sigma$) to determine the upper and lower
   limits of the parameters. The  constraint results are shown in 
   Figure \ref{fig:1} and summarized in Table \ref{tab:5}.

   \begin{figure*}
      \centering
      \subfigure{
         \includegraphics[width=0.3\textwidth]{sne_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.3\textwidth]{bao_sne_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.3\textwidth]{sne_2.pdf}
      }
      \subfigure{
         \includegraphics[width=0.3\textwidth]{bao_sne_2.pdf}
      }
      \subfigure{
         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_2.pdf}
      }
      \caption{The constraint result from the supernovae Ia data
      (left), the BAO + SNe Ia data (middle) and the BAO + SNe Ia + OHD data (right).}
      \label{fig:1}
   \end{figure*}

   \begin{table*}
      \centering
      \begin{tabular}{lccc}
         \hline\hline
         Model 1 & SNe Ia & BAO + SNe Ia & BAO + SNe Ia + OHD \\
         \hline
         $\Omega_{2,0}$ & $0.380_{-0.020}^{+0.020}$
          & $0.3078_{-0.0067}^{+0.0053}$ & $0.3079_{-0.0067}^{+0.0051}$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $<-2.73$ 
         & $<-3.70$  & $<-3.71$ \\
         $\log_{10}(M_x/$GeV) & $>-9.26$
         & $>-8.24$ & $>-8.26$ \\
         \hline
      \end{tabular}
      \caption{The constraint results of Model 1.}
      \label{tab:5}
   \end{table*}

   The SNe Ia dataset gives a value $\Omega_{2,0} \simeq 0.38$. The constraint result to Pantheon+
   SNe Ia dataset in the flat $\Lambda$CDM model is $\Omega_{m} \simeq 0.33$ (\cite{Borghi_2022}),

   We use the most combined dataset of OHD + SNe Ia + BAO to give a stringent lower limit
   of $\log_{10}(M_x/$GeV) $\simeq -8.26$ at $2\sigma$ level, similar to the 
   sub-MeV mass of the interacting dark matter.

@@

   \begin{figure*}
      \centering
      \subfigure{
         \includegraphics[width=0.3\textwidth]{sne_widm_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.3\textwidth]{bao_sne_widm_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_widm_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.3\textwidth]{sne_widm_2.pdf}
      }
      \subfigure{
         \includegraphics[width=0.3\textwidth]{bao_sne_widm_2.pdf}
      }
      \subfigure{
         \includegraphics[width=0.3\textwidth]{ohd_sne_bao_widm_2.pdf}
      }
      \caption{The constraint result from the supernovae Ia data
      (left), the BAO + SNe Ia data (middle) and the BAO + SNe Ia + OHD data (right).}
   \end{figure*}

   \begin{table*}
      \centering
      \begin{tabular}{lccc}
         \hline\hline
         Model 2 & SNe Ia & SNe Ia + BAO
          & OHD + SNe Ia + BAO \\
         \hline
         $\Omega_{2,0}$ & $0.215_{-0.073}^{+0.10}$
          & $0.2940_{-0.0076}^{+0.0076}$ & $0.2945_{-0.0075}^{+0.0075}$ \\
         $n$ & $-0.82_{-0.45}^{+0.29}$
          & $-0.43_{-0.10}^{+0.10}$ & $-0.42_{-0.11}^{+0.11}$ \\
         $w_{\text{IDM}}$ & $-0.73_{-0.10}^{+0.15}$
          & $-0.86_{-0.03}^{+0.03}$ & $-0.86_{-0.04}^{+0.04}$ \\
         \hline
      \end{tabular}
      \caption{The constraint results of Model 2.}
      \label{tab:6}
   \end{table*}

@@

   \begin{equation}
      Const=\mathcal{F}(-\infty)\equiv\lim_{x\to-\infty}\mathcal{F}(x)=
      \frac{\kappa C_1\ln\kappa C_1}{9H_0^4\Omega_{1,0}^2-4H_0^2\Omega_{1,0}(\kappa C_1)^2}.
   \end{equation}
   The initial time of today $t_0$ can be easily given as
   \begin{equation}
      t_0=2H_0^2\Omega_{1,0}[\mathcal{F}(-\infty)-\mathcal{F}(-H_0)],
   \end{equation}
   and the redshift $z_{\max}$ can be calculated as
   \begin{equation}
      z_{\max}=\exp\left[2H_0^2\Omega_{1,0}\int_{-\infty}^{-H_0}[\mathcal{F}(-\infty)
      -\mathcal{F}(x)]\mathrm{d}x+H_0t_0\right]-1,
   \end{equation}
   and $z_{\max}$ is also a function of $\Omega_{2,0}, \kappa C_1$ and $H_0$.
   \begin{figure}
      \centering
      \includegraphics[width=0.7\textwidth]{zmax.pdf}
      \caption{The redshift $z_{\max}$ as $H_0=70$ km/s/Mpc}
   \end{figure}
